Naming Objects in Real-world Images: A survey and A new \sz{linguistically motivated????} collection

### 2019-11-09 papers/EMNLP2019/reviews_author_response.txt

Response to Review #1:

The main contribution of our dataset is that it systematically collects names for objects; we have 25K objects with 33-36 annotations. There is, to our knowledge, no other dataset with similar characteristics:

- Previous datasets, including those in the references provided in the review, contain one or few expressions per object (e.g., only 10.7% of ReferIt provides 2 or more expressions; the datasets based on COCO have between *** and *** expressions on average).

- Previous datasets provide either referring expressions or object descriptions; we collect object names. This is a phenomenon underlying referring expressions, so to speak; to properly understand how the choice of the object name interacts with the choice of attributes (modifiers, prepositional phrases), one needs to know which name variants exist and how they are related. This is why we study object naming as a separate phenomenon.

***THIS PARAGRAPH IS A CANDIDATE TO BE LEFT OUT IF WE ARE SHORT ON SPACE*** The first paper you point out (Kazemzadeh et al., 2014, page 791) distinguishes also between difference of referring expressions and canonical names (entry-level categories); however, it adopts two assumptions standard in Psycholinguistics that we show not to hold (that naming variants are related hierarchically, and that there is a largely instance-invariant entry-level or canonical name). VisualGenome contains region descriptions (often containing modifiers) instead of names, and only one or very few per region.

> Thus, the core question of this paper, "Do Objects in Real-World Images Have a Canonical Name?", will not impactful (at least, in the NLP community). I feel that people already know "no".

First, the answer according to our data is nuanced (on average, the most frequent name covers 75% of the responses, which is quite a large agreement; we also find quite a bit of variation); second, to the best of our knowledge there is no study that empirically addresses this question on a large scale; third, we provide evidence that the main source of naming variation studied so far, variation along a taxonomical hierarchy, accounts for very little of the data.

L237: Balancing was conducted precisely to avoid bias: Larger seeds subsumed more different VG object classes than smaller seeds. Any dataset of course has some bias; we chose categories that are fairly common in visual data.

We exploited the meta-annotation for filtering after round 0: we excluded around 6K objects that had no clear bounding boxes or were occluded. After that, for the rest of the annotations of the remaining 25K objects, we did not gather meta-annotations.

Please find the answers on the experiment in Section 5 in the general answers to reviews below.

Response to Review #2:

We chose VG over COCO because we wanted to cover a wider range of categories. It is a well-accepted dataset in the community and in our own analyses of the VG data in our sample we did not identify much noise.

We were considering using directly the MSCOCO labels for the MSCOCO images (recall that Visual Genome was built on top of MSCOCO), but decided against it for the following reasons: MSCOCO only contains 80, easy to separated categories of an arbitrary level of specificity (person, dog, tie, donut, ...).  This does result in little noise, but also in images not as densely labeled as in VG. 
In sum, linguistically analysing object naming variations across many different domains and classes, and allowing researchers to analyse the influence of the context (objects and their domain or category) would not be possible with MSCOCO annotations.

Indeed, reporting results on the training data (in addition to results on unseen images) is nonstandard. We included these results because we obtain a higher accuracy on ManyNames than on the original training data, as noted in your review, which is a striking result. We will rephrase to clarify, and reorganize the table such that it is clear that the results on the test partition are the main results.

Response to Review #3:

Thank you, we will revise the presentation of the tables as you suggested.

General Response to Reviewers:

- Thank you for the constructive feedback.

- We will make the ManyNames dataset publicly available upon acceptance of the paper.

Response to Chairs

@@

- VisualGenome has been used especially in Language+Vision research (REFS).

Experimental questions:

The experiment shows the following: 
With our experiment in Section 5 and its results we hope to spur discussion and reconsideration of the current standard in Language & Vision research which works on modeling the human way of naming and referring to real-world objects. 
In particular:
- The evaluation against a single label may be ill-defined, since this label may not be the one a majority of humans would agree on for the given instance (=> we need many more annotations for a single instance to obtain a canonical name) 
- To assess the ability to "recognize" an object (against other models), it may not be conclusive to do this based on a single label, but instead on what labels it predicts as most probable.

Regarding the experiment specifically: 
Please recall that we only compared on the shared set of 1,254 name types, which is a fraction of those in ManyNames. We hope that testing and comparing fine-tuned models on ManyNames would be useful to evaluate their ability to mimic human naming variation, and further to compare models against their ability to distinguish variants from for humans unreasonable/inconstistent mistakes.

### 2019-11-09 papers/LREC2020/data-collection.tex
revised data collection

We take data from \vg~\cite{krishna2016visualgenome}, which
% aims to provide a full set of descriptions of the scenes which images depict in order to spur complete scene understanding. 
contains a dense region-based labeling of $108$K~images with, inter alia, objects, attributes and relationships,  %object descriptions, attributes, and relationships, as well as question-answer pairs, 
all linked to WordNet synsets \cite{fellbaum1998wordnet}.
\vg suits our purpose of collecting names for naturalistic instances of common objects, as it has images of varying complexity, with close-ups as well as images with many objects.
%As common in Computer Vision, O
Objects are localized as 
%identified via
 bounding boxes, as in Figure~\ref{fig:cake}.% 
\footnote{We use image and object interchangeably in the following, since we only selected one target object per image (i.e., each object and image in VG is chosen at most once).}

\subsection{Sampling of Instances}
\label{ssec:sampling}
 % of frequent classes/names in  \vgenome, which, at the same time, have been frequently/commonly studied in the psycholinguistic literature. 
%Criteria: From CV: select images depicting objects with relatively frequent names; From CogSci: select objects which have been frequently studied in cognitive science/psychological norming studies; we chose McRae et al. as basis.
We selected images from seven domains: six based on McRae et al.'s  (\citeyear{mcrae2005semantic}) feature norms, a dataset widely used in Psycholinguistics that comprises common objects of different categories (e.g.,~\textsc{animals}, \textsc{furniture}), and \textsc{person}, because it is a very frequent category in \vg.
% We start from the concepts of McRae et al.'s feature norms (REF), which are common objects of different categories (e.g.,~\textsc{animals}, \textsc{furniture}) and, as such, have a high overlap with standard datasets of object norming studies (REFS).
% We added the \textsc{person} category because it is very frequent category in \vgenome.

Within each domain, we aimed at collecting instances at different taxonomic levels  to cover a wide range of phenomena, but this is not straightforward because ontological taxonomies do not align well with the lexicon (for instance, \textit{dog} and \textit{cow} are both mammals, but \textit{dog} has many more common subcategories), and most domains are not organized in a clear taxonomy %in the first place 
(e.g.\ \textsc{home}).
% Standard taxonomies do not align well with name variability; for instance, people use more varied names for types of dogs than for types of cows, while both dogs and cows are mammals.
Instead, we defined a set of synsets ($52$\ in total) that we would use to collect our object instances from \vg, balancing variability.
From the set of synsets that match or subsume the concepts in the McRae norms, we kept those with a high number of \vg object instances of different names.
For example, \vg instances subsumed by McRae's \textsl{dog} were named \textsl{beagle, greyhound, puppy, bulldog}, etc., while McRae's \textsl{duck}, \textsl{goose}, or \textsl{gull} did not have name variants in \vg, so we kept \textsl{dog} and \textsl{bird} (which subsumes \textsl{duck}, \textsl{goose}, or \textsl{gull}) as collection synsets.

We then retrieved all VG images depicting an object whose name matches or is subsumed by words in one of these synsets; we refer to these words as \textit{seeds} ($450$\ in total).
We did not consider objects with names in plural form, with parts-of-speech other than nouns\footnote{We obtained tags with CoreNLP \cite{manning2014stanford}.}, or that were multi-word expressions (e.g.,~\textsl{pink bird}). 
We further only considered objects whose bounding box covered~\mbox{$20-90\%$} of the image area.
% We based the definition of our set of nodes on the WN (REF) synsets of the McRae concepts (e.g.,~dog, duck, goose, gull), the nominal WordNet hierarchy, and the frequency distribution of the VG object names' synsets.\footnote{TODO: need to be clear from the general description of VG that the frequ. of instances labeled with the synset of the object name is meant.} 
% First, we selected a set of collection node candidates---synsets which match (e.g.,~\textsl{dog, duck, goose, gull}) or subsume (e.g.,~\textsl{mammal, bird}) the McRae synsets\footnote{Specific synset IDs, e.g.,~dog.n.01, are omitted for readability.}. 
% From these candidates we kept those as collection nodes which had a high frequency of VG object instances of different names. For example, VG instances  subsumed by McRae's \textsl{dog} were named \textsl{beagle, greyhound, puppy, bulldog}, etc., while McRae's \textsl{duck, goose}, or \textsl{gull} did not have name variants in VG, so we kept \textsl{dog} and \textsl{bird} as collection nodes.
%\paragraph{Collection of instance candidates}
% Goal of above procedure was the collection of instances of selected object classes---our nodes--- whose VG names correspond to or subsume (are hypernyms of) a McRae concept, and whose object names differ, that is, of which we can expect that people possess different names for them (e.g.,~\textsl{duck, goose, gull} for \textsl{bird}).
% \paragraph{Sampling of instances}
Because of the Zipfian distribution of names, and to balance the collection, we sampled instances depending on the size of the seeds: up to $500$\ instances for seeds with up to $800$\ objects, and up to $1000$\ instances for larger seeds. %\textbf{double-check}
This yielded a dataset of\ $31,093$~instances, which was further pruned during annotation. 
See Section\ \ref{ssec:elicitation} and the Supplemental Material for details on the pruning. 
% \begin{itemize}
% \item rows: domains (if we go for long paper: then one row per collection node?)
% \item columns:
%   \begin{enumerate}
%   \item \# collection nodes
%   \item collection nodes (list)
%   \item \# unique VG names
%   \item example VG names
%   \item \# unique objects
%   \item \# unique images (? not sure if necessary; maybe only one of unique {objects, images})
%   \end{enumerate}
% \end{itemize}

\subsection{Elicitation Procedure}
\label{ssec:elicitation}
To elicit object names, we set up a crowdsourcing task on Amazon Mechanical Turk (AMT).
In initial pilot studies, we found object identification via bounding boxes to be problematic.
In some cases, the bounding box was not clear; in others, AMT workers named objects that were more salient than the one signaled by the box (for instance, for a box around a jacket, the man wearing it).
We took special care of minimizing this issue in two ways: Specifying the instructions such that workers pay close attention to what object is being indicated in the box, and pruning the set of images via an initial collection round (9 workers per task, i.e.,\ 9 names/object) in which we allowed workers to indicate whether the object was occluded or the box unclear. 
%The Appendix~\ref{app:instructions} contains the task instructions and details about the pruning and data procedure.
We eliminated around $5.5$K\ images based on pruning, obtaining the final dataset with $25,596$\ images. 
(We refer to the Supplemental Material for the task instructions and more details on the pruning and the dataset.) 
We then did 3 more collection rounds, and shuffled the set of images per task between each round. 
Workers could only participate in one round, to avoid workers annotating an instance more than once. 
We obtained a total of 36 names per image (i.e.,\ object).
As will become clear in the analysis, while object identification remains an issue despite these precautions, most mismatches between \vg annotations  and our data cannot be considered mistakes, and the annotation results have significant implications for the study of object naming in L\&V (see discussion in Sections~\ref{sec:analysis} and \ref{sec:modeling}).
Overall $841$\ workers took part in the data elicitation, with a median of  $261$\ instances \mbox{($\textrm{range}=[9,17K]$)} per worker.
%\cs{Maybe say something about the rejections, if space permits it.}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:

>>>>

\begin{table*}[htp]
	\small
	\centering
	\begin{tabular}{lp{14cm}}
			\toprule
			Domain & \multicolumn{1}{c}{Synsets}\\
			\midrule			
			buildings      &  house$_1$ (364), bridge$_1$ (297), shelter$_1$ (169), restaurant$_1$ (58),
                                         outbuilding$_1$ (31), hotel$_1$ (19), housing$_1$ (17), place\_of\_worship$_1$ (12)     \\
			people         & woman$_1$ (1768), man$_1$ (1167), male\_child$_1$ (853), athlete$_1$ (396),
			 child$_1$ (333), creator$_2$ (11), professional$_1$ (5)    \\
			home           &  furnishing$_2$ (5,355), vessel$_3$ (525), kitchen\_utensil$_1$ (132), crockery$_1$ (92),
			cutlery$_2$ (82), tool$_1$ (72), lamp$_1$ (34)    \\
			clothing       &  shirt$_1$ (968), overgarment$_1$ (786), dress$_1$ (199), headdress$_1$ (135),
                                         neckwear$_1$ (65), robe$_1$ (27), glove$_2$ (7), footwear$_1$ (5)    \\
			vehicles       &  aircraft$_1$ (1208), train$_1$ (957), car$_1$ (727), motorcycle$_1$ (564),
                                         truck$_1$ (559), boat$_1$ (499), ship$_1$ (38)    \\
			food           &  dish$_2$ (812), baked\_goods$_1$ (770), foodstuff$_2$ (280), vegetable$_1$ (48),
                                         edible\_fruit$_1$ (42), beverage$_1$ (23)   \\
			animals\_plants & ungulate$_1$ (2037), horse$_1$ (833), feline$_1$ (763), dog$_1$ (688)
			bird$_1$ (389), flower$_1$ (44), rodent$_1$ (27), insect$_1$ (12), fish$_1$ (11)\\
			\bottomrule
		\end{tabular}
		\caption{Overview of the ManyNames dataset: Synset nodes for each domain (subscript indicates synset number; number of instances in parentheses).
                  \label{tab:overview_dataset2}}
	\end{table*}

\begin{table*}[htp]
	\small
	\centering
	\begin{tabular}{@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l}
		\toprule
		vehicles &            food & animals\_plants &           home &        buildings &             people &      clothing \\
		\midrule
		train (954) &  pizza (518) &  giraffe (915) &  bed (888) &  house (340) &  boy (853) &  shirt (904) \\
		car (642) &  cake (261) &  horse (822) &  bench (714) &  bridge (274) &  man (806) &  jacket (451) \\
		plane (485) &  bread (186) &  cat (754) &  table (687) &  dugout (91) &  woman (766) &  coat (267) \\
		airplane (479) &  sandwich (153) &  dog (654) &  desk (672) &  tent (53) &  girl (650) &  dress (190) \\
		motorcycle (466) &  bun (143) &  zebra (461) &  counter (516) &  restaurant (33) &  lady (342) &  hat (77) \\
		% truck (465) &  cheese (110) &  cow (324) &  couch (366) &  overpass (23) &  guy (330) &  t-shirt (62) \\
		% boat (450) &  donut (78) &  bird (295) &  chair (365) &  grill (22) &  child (230) &  tie (51) \\
		% jet (106) &  salad (70) &  sheep (216) &  carpet (307) &  garage (18) &  batter (110) &  blazer (43) \\
		% aircraft (85) &  sauce (68) &  bull (48) &  bowl (219) &  hotel (16) &  kid (85) &  hood (26) \\
		% van (76) &  apple (33) &  flower (40) &  curtain (182) &  castle (14) &  skateboarder (80) &  cap (20) \\
		\bottomrule
	\end{tabular}
	\caption{Overview of the ManyNames dataset: Top 5 VG names for each domain (number of instances in parentheses). %\textbf{double-check}
		\label{tab:overview_dataset1}}
\end{table*}

\begin{figure*}[htp]
  \centering
  \includegraphics[width=1.5\columnwidth]{figures/round0.png}
  \caption{Instructions for AMT annotators for the first round.}
  \label{fig:instructions1}
\end{figure*}

We take data from \vgenome~\cite{krishna2016visualgenome}, which
contains a dense region-based labeling of $108$K~images with, inter alia, object names, attributes and relationships,
all linked to WordNet synsets \cite{fellbaum1998wordnet}.
\vg suits our purpose of collecting names for naturalistic instances of common objects, as it has images of varying complexity, with close-ups as well as images with many objects.
As common in Computer Vision, objects are localized as bounding boxes, as in Figure~\ref{fig:cake}.% 
\footnote{We use image and object interchangeably in the following, since we only selected one target object per image (i.e., each object and image in VG is chosen at most once).}

\subsection{Sampling of Instances}
\label{ssec:sampling}

%Criteria: From CV: select images depicting objects with relatively frequent names; From CogSci: select objects which have been frequently studied in cognitive science/psychological norming studies; we chose McRae et al. as basis.
We selected images from seven domains: six based on McRae et al.'s  (\cite{mcrae2005semantic}) feature norms, a dataset widely used in Psycholinguistics that comprises common objects of different categories (e.g.,~\textsc{animals}, \textsc{furniture}), and \textsc{person}, because it is a very frequent category in \vg.
% We start from the concepts of McRae et al.'s feature norms (REF), which are common objects of different categories (e.g.,~\textsc{animals}, \textsc{furniture}) and, as such, have a high overlap with standard datasets of object norming studies (REFS).
% We added the \textsc{person} category because it is very frequent category in \vgenome.

Within each domain, we aimed at collecting instances at different taxonomic levels to cover a wide range of phenomena, but this is not straightforward because ontological taxonomies do not align well with the lexicon (for instance, \textit{dog} and \textit{cow} are both mammals, but \textit{dog} has many more common subcategories), and most domains are not organized in a clear taxonomy in the first place (e.g.\ \textsc{home}).
Instead, we defined a set of synsets ($52$\ in total; listed in Table~\ref{tab:overview_dataset2}) that we used to collect our object instances from \vg.

From the set of synsets that match or subsume the concepts in the McRae norms, we kept those with a high number of \vg object instances of different names.
For example, \vg instances subsumed by McRae's \textsl{dog} were named \textsl{beagle, greyhound, puppy, bulldog}, etc., while McRae's \textsl{duck}, \textsl{goose}, or \textsl{gull} did not have name variants in \vg, so we kept \textsl{dog} and \textsl{bird} (which subsumes \textsl{duck}, \textsl{goose}, or \textsl{gull}) as collection synsets.
\gbt{Just to clarify: we also collected objects named \textsl{duck}, \textsl{goose}, or \textsl{gull}, right? Not only \textsl{bird}?}

We then retrieved all VG images depicting an object whose name matches or is subsumed by words in one of these synsets; we refer to these words as \textit{seeds} ($450$\ in total).
We did not consider objects with names in plural form, with parts-of-speech other than nouns\footnote{We obtained tags with CoreNLP \cite{manning2014stanford}.}, or that were multi-word expressions (e.g.,~\textsl{pink bird}). 
We further only considered objects whose bounding box covered~\mbox{$20-90\%$} of the image area.
% We based the definition of our set of nodes on the WN (REF) synsets of the McRae concepts (e.g.,~dog, duck, goose, gull), the nominal WordNet hierarchy, and the frequency distribution of the VG object names' synsets.\footnote{TODO: need to be clear from the general description of VG that the frequ. of instances labeled with the synset of the object name is meant.} 
% First, we selected a set of collection node candidates---synsets which match (e.g.,~\textsl{dog, duck, goose, gull}) or subsume (e.g.,~\textsl{mammal, bird}) the McRae synsets\footnote{Specific synset IDs, e.g.,~dog.n.01, are omitted for readability.}. 
% From these candidates we kept those as collection nodes which had a high frequency of VG object instances of different names. For example, VG instances  subsumed by McRae's \textsl{dog} were named \textsl{beagle, greyhound, puppy, bulldog}, etc., while McRae's \textsl{duck, goose}, or \textsl{gull} did not have name variants in VG, so we kept \textsl{dog} and \textsl{bird} as collection nodes.
%\paragraph{Collection of instance candidates}
% Goal of above procedure was the collection of instances of selected object classes---our nodes--- whose VG names correspond to or subsume (are hypernyms of) a McRae concept, and whose object names differ, that is, of which we can expect that people possess different names for them (e.g.,~\textsl{duck, goose, gull} for \textsl{bird}).
% \paragraph{Sampling of instances}
Because of the Zipfian distribution of names, and to balance the collection, we sampled instances depending on the size of the seeds: up to $500$\ instances for seeds with up to $800$\ objects, and up to $1000$\ instances for larger seeds. This yielded a dataset of\ $31,093$~instances, which was further pruned during annotation, as follows.
Table~\ref{tab:overview_dataset1} shows the top 5 \vgenome names in each of the domains.
% \begin{itemize}
% \item rows: domains (if we go for long paper: then one row per collection node?)
% \item columns:
%   \begin{enumerate}
%   \item \# collection nodes
%   \item collection nodes (list)
%   \item \# unique VG names
%   \item example VG names
%   \item \# unique objects
%   \item \# unique images (? not sure if necessary; maybe only one of unique {objects, images})
%   \end{enumerate}
% \end{itemize}

\subsection{Elicitation Procedure}
\label{ssec:elicitation}

To elicit object names, we set up a crowdsourcing task on Amazon Mechanical Turk (AMT).
In initial pilot studies, we found object identification via bounding boxes to be problematic.
In some cases, the bounding box was not clear; in others, AMT workers named objects that were more salient than the one signaled by the box (for instance, for a box around a jacket, the man wearing it).
We took special care of minimizing this issue in two ways: Specifying the instructions such that workers pay close attention to what object is being indicated in the box, and pruning the set of images via an initial collection round (9 workers per task, i.e.,\ 9 names/object) in which we allowed workers to indicate whether the object was occluded or the box unclear (see Figure~\ref{fig:instructions1} for the instructions).

%We eliminated around $5.5$K\ images based on pruning, obtaining the final dataset with $25,596$\ images.
After the first round, based on the opt-out annotation, we kept images that met all the following conditions (thresholds were estimated via manual inspection): (i) they were not marked as occluded by any subject; (ii) ``Bounding box is unclear'' was marked at most twice; (iii) at most 17\% of elicited names were in plural form (to remove cases where the bounding box contains several objects); (iv) the most frequent elicited name is of the same domain as the \vgenome name.
This yielded $25,596$ images (we discarded $5,497$).
We then did 3 more collection rounds, shuffling the set of images per task between each round.
Figure~\ref{fig:instructions2} shows the instructions for these rounds; they were accompanied by a FAQ solving common issues. 
Workers could only participate in one round, to avoid workers annotating an instance more than once. 
We obtained a total of 36 names per object.
Overall $841$\ workers took part in the data elicitation, with a median of  $261$\ instances \mbox{($\textrm{range}=[9,17K]$)} per worker.

\begin{figure*}[htp]
  \centering
  \includegraphics[width=1.5\columnwidth]{figures/round1+_p1.png}
  \caption{Instructions for AMT annotators for rounds~$2$ to~$4$.}% They were accompanied by the FAQ in Figure~\ref{fig:faq}}
  \label{fig:instructions2}
\end{figure*}

% \begin{figure*}[htp]
%   \centering
%   \includegraphics[width=1.5\columnwidth]{figures/round1+_p2.png}
%   \caption{FAQ accompanying the instructions for AMT annotators for rounds~$2$ to~$4$.}
%   \label{fig:faq}
% \end{figure*}

%\cs{Maybe say something about the rejections, if space permits it.}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "lrec2020naming"
%%% End:
